---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# staRtup

<!-- badges: start -->
<!-- badges: end -->

The goal of staRtup is to easily create folders when starting-up your R Project

## Installation

You can install the released version of staRtup from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("staRtup")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("daleericko/staRtup")
```
## Example

This is a basic example which shows how easy it is to start your project with the four basic folder: data-raw, data-output, R-scripts, and resources. 

```{r example, message=FALSE}
library(staRtup)

staRtup()
```

Just running the function above will create those directories. If any or all of the directories already exist, a message will display letting the user know that the folder exists.

## Why staRtup?

The best thing you can do as a coder / programmer is keep your code and relevant files in an organized fashion. Every time I start an R project, I know if will use these four folders, so what better way to save time than to just have this in a function? 

\###
